\titleFr{Publications}
\titleEn{Publications}
\class{research}

#job
\publication{Kevin Lalumi\`ere, Interaction between Move Semantic and Copy Elision in C++, https://source.coveo.com/2018/11/07/interaction-between-move-semantic-and-copy-elision-in-c++/, (2018).}

#Doctorat
\publication{Benjamin J. Chapman, Eric I. Rosenthal, Joseph Kerckhoff, Bradley A. Moores, Leila R. Vale, J. A. B. Mates, Gene C. Hilton, Kevin Lalumi\`ere, Alexandre Blais, and K. W. Lehnert, Widely Tunable On-Chip Microwave Circulator for Superconducting Quantum Circuits, Phys. Rev. X 7, 041043 (2017).}
\publication{J. Kerckhoff, K. Lalumi\`ere, B. J. Chapman, A. Blais and K. W. Lehnert, On-Chip Superconducting Microwave Circulator from Synthetic Rotation, Phys. Rev. Applied 4, 034002 (2015).}
\publication{K. Lalumi\`ere and A. Blais, Remote Controlled Entanglement, Physics 7, 45 (2014).}
\publication{A. F. van Loo, A. Fedorov, K. Lalumi\`ere, B. C. Sanders, A. Blais, and A. Wallraff, Photon-Mediated Interactions Between Distant Artificial Atoms, Science 342, 6165 pp. 1494 (2013).}
\publication{K. Lalumi\`ere, B. C. Sanders, A. F. van Loo, A. Fedorov, A. Wallraff, and A. Blais, Input-output theory for waveguide qed with an ensemble of inhomogeneous atoms, Phys. Rev. A 88, 043806 (2013).}

#Maîtrise
\publication{K. Lalumi\`ere, J. M. Gambetta, and A. Blais, Tunable joint measurements in the dispersive regime of cavity qed, Phys. Rev. A 81, 040301 (2010).}

#BAC
\publication{P. Xue, B. C. Sanders, A. Blais, and K. Lalumi\`ere, Quantum walks on circles in phase space via superconducting circuit quantum electrodynamics, Phys. Rev. A 78, 042334 (2008).}
