\titleFr{Pr\'esentations}
\titleEn{Contributed Talks}
\class{research}

#Doctorat
\talk{Interactions between superconducting qubits mediated by travelling photons, CIFAR Meeting, Orford(Qc), Canada, 2013.}
\talk{Interactions between superconducting qubits mediated by travelling photons, INTRIQ Meeting, Bromont(Qc), Canada, 2013.}
\talk{Strong Interaction between 2 qubits in a Transmission Line, CONFETI Meeting, Orford(Qc), Canada, 2013.}
\talk{Tuning from coherent interaction to super and subradiance with artificial atoms in a 1D waveguide, APS March Meeting, Baltimore(Maryland), USA, 2013.}
\talk{Tuning from coherent interaction to super and subradiance with artificial atoms in a 1D waveguide, ACP Meeting, Montreal(Qc), Canada, 2013.}
\talk{Waveguide QED with an ensemble of inhomogeneous atoms, CIFAR Quantum Cavities Workshop, Montreal(Qc), Canada, 2013.}
\talk{Quantum optics in a transmission line, CONFETI Meeting, Orford(Qc), Canada, 2012.}
\talk{Cooperative effects for Qubits in a Transmission Line: Theory, APS March Meeting, Boston(Massachusetts), USA, 2012.}
\talk{Parity Measurement in Circuit Quantum Electrodynamics, CONFETI Meeting, Sutton(Qc), Canada, 2011.}
\talk{Introduction \`a l'informatique quantique impl\'ement\'ee \`a l'aide de qubits supraconducteurs, ACFAS Meeting, Sherbrooke(Qc), Canada, 2011.}
\talk{Tunable joint measurements in the dispersive regime of circuit QED, Quantum Machines Summer School, Les Houches, France, 2011.}

#Maîtrise 
\talk{Tunable joint measurements in the dispersive regime of cavity QED, APS March Meeting, Portland(Oregon), USA, 2010.}
\talk{Parity Measurement of Superconducting Qubits in circuit QED, INTRIQ Meeting, Jouvence(Qc), Canada, 2010.}
